---
title: "Descriptive statistics of Discouraged worker"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::pdf_document2:
    toc: no
    toc_depth: 3
    keep_tex: no
  bookdown::word_document2:
    fig_caption: yes
  word_document:
    toc: no
    toc_depth: '3'
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	fig.align = "center",
	fig.height = 3,
	fig.width = 5,
	message = FALSE,
	warning = FALSE,
	dpi = 300
)

library(here)
library(tidyverse)
library(scales)
library(janitor)

# Theme update
theme_set(theme_bw())
theme_update(plot.margin = unit(c(1,1,1,1), "cm"))

# Setting Directories ----

# Sub-directories
rawdata <- paste0(here::here(), "/data/raw/main_raw/")
scripts <- paste0(here::here(), "/data/scripts/main_scripts/")
cleandata <- paste0(here::here(), "/data/clean/main_clean/")
figures <- paste0(here::here(), "/data/output/figures/")

# Functions to plots different types of data ----
source(paste0(here(),"/data/scripts/","tab_plot_functions_new.R"))

# Colour Palette
cbp1 <- c("#003f5c","#00c698","#58508d","#bc5090","#0069c0","#ff6361","#ffa600")

# Loading datasets
load(paste0(cleandata, "SurveyCleanData.RData"))

df_female_wob <- df_female %>% 
  filter(!district_name == "Barmer")
df_male_wob <- df_male %>% 
  filter(!district_name == "Barmer")

# Disc_Worker: 
# Used to work- Consider those who quit. Remove those whose primary reason for quitting was illness and education.Retain those who are willing and not looking for work. Lastly, retain those who are not willing to work.
# Never worked: Retain those who are willing and not looking for work. Include those who are not willing to work for reasons other than education and illness

df_disc <- df_female_wob %>% 
  mutate(disc_worker = as.factor(case_when(wp22_looking_work == "No" | wp22_work_not_willing_illness != 1 & wp22_work_not_willing_education != 1 |(wp23_quit_higher_education != 1 & wp23_quit_health_issues != 1 & wp23_looking_work == "No") | (wp23_quit_higher_education != 1 & wp23_quit_health_issues != 1 & wp23_work_if_available == "No") ~1,
                                           TRUE~0)))
df_disc_only <- df_disc %>% 
  filter(disc_worker == 1)

write.csv(df_disc, paste0(cleandata, "discouraged.csv"))

# Cleaning variables----

df_disc <- df_disc %>% 
  ungroup() %>% 
  mutate(
    Married = as.factor(case_when(marital_status == "Married" ~ "Married",
                                  TRUE ~ "Not Married")))
df_disc <- df_disc %>% 
  mutate(
    social_category = as.character(social_category),
    social_category = case_when(social_category %in% c("Do Not Know", "Refused to Answer") ~ "Others",
                                TRUE~social_category),
    social_category = factor(social_category, levels = c("General","OBC","SC","ST","Others")),
    primary_income_earner = as.factor(case_when(primary_income_earner == "No-one" ~ "No-one",
                                                primary_income_earner == "Spouse" ~ "Spouse", 
                                                primary_income_earner == "Self" ~ "Self",
                                                TRUE~ "Others")),
    highest_education = case_when(highest_education %in% c("No education")~"Not Literate",
                              highest_education %in% c("class 1", "class 2","class 3","class 4","class 5")~"Primary", 
                              highest_education %in% c("class 6","class 7","class 8")~"Secondary",
                              highest_education %in% c("class 9","class 10")~"Secondary",
                              highest_education %in% c("class 11","class 12")~"Higher Secondary",
                              highest_education %in% c("Graduate","Diploma")~"Graduate",
                              highest_education %in% c("Post Graduate","Higher")~"Post Graduate and Above",
                               TRUE~NA_character_),
         highest_education = factor(highest_education,  levels = c("Not Literate", "Primary", "Secondary", "Higher Secondary","Graduate","Post Graduate and Above")),
    children_household = as.factor(children_household),
    studying_household = as.factor(studying_household),
    casual_daily_household = as.factor(casual_daily_household),
    casual_piece_household = as.factor(casual_piece_household),
    permanent_work_household = as.factor(permanent_work_household)) %>% 
  rename("Social Category" = "social_category",
         "Household Head" = "head_household",
         "Primary Income Earner" = "primary_income_earner",
         "Education of PIE" = "highest_education")

# Functions----
plot_disc_area <- function(var_name){
  tab <- df_disc %>% 
  group_by(area_actual, !!sym(var_name)) %>% 
  mutate(T_AS = n()) %>% 
  group_by(area_actual, disc_worker, !!sym(var_name), .drop = F) %>% 
  summarise(N = n(),
            Percentage = round(N/first(T_AS)*100,2)) %>%
  filter(disc_worker == 1) %>% 
  adorn_totals()

ggplot(data = tab %>% filter(area_actual != "Total"), mapping = aes(x = !!sym(var_name), y = Percentage, fill = area_actual))+
  geom_col(position = "dodge")+
  geom_text(aes(label = Percentage),position=position_dodge(width=0.75), vjust=-0.25, size=2)+
  theme_bw() +
    scale_x_discrete(labels = wrap_format(12))+
    theme(axis.text = element_text(size = 7),
          axis.title = element_text(size = 7),
          plot.title = element_text(size = 9),
          legend.title = element_text(size = 7),
          legend.text = element_text(size = 6))+ 
    theme( legend.position = "bottom",
           strip.background = element_rect(colour="white"))
}

tab23_factors <- function(dataframe, varname){
  tab <- df_disc %>% 
  select(starts_with("wp23_quit"), !!sym(varname)) %>% 
  select(-c(contains("_rank_"), contains("_other"))) %>% 
  pivot_longer(cols = starts_with("wp23"),
               names_to = "Reasons",
               values_drop_na = T) %>%
  group_by(Reasons) %>% 
  mutate(
    Total = sum(value)
  ) %>% 
  group_by(!!sym(varname), Reasons) %>% 
  summarise(
    Frequency = sum(value)
    # Percentage = round(Frequency/first(Total)*100,2)
  ) %>% 
  pivot_wider(names_from = !!sym(varname), 
              values_from =  c(Frequency))
  return(tab)
}

table_kable <- function(tableframe, caption) {
  
  knitr::kable(tableframe, caption = caption, booktabs = TRUE) %>%
    kableExtra::kable_styling(font_size = 10,latex_options = "hold_position", full_width = FALSE) %>% 
    row_spec(0, bold = T) %>% # format last row
    column_spec(1, italic = T)
}


tab22_factors <- function(dataframe, varname){
  tab <- df_disc %>% 
  select(starts_with("wp22_work_not_willing"), !!sym(varname)) %>% 
  select(-c(contains("_rank_"), contains("others"))) %>% 
  pivot_longer(cols = starts_with("wp22"),
               names_to = "Reasons",
               values_drop_na = TRUE) %>%
  group_by(Reasons) %>% 
  mutate(
    Total = sum(value)
  ) %>% 
  group_by(!!sym(varname), Reasons) %>% 
  summarise(
    Frequency = sum(value)
    # Percentage = round(Frequency/first(Total)*100,2)
  ) %>% 
  pivot_wider(names_from = !!sym(varname), 
              values_from =  c(Frequency)) 
  return(tab)
}

```

\newpage

## Definition of Discouraged Worker

In the study, the following two types of workers are termed are discouraged: 1) Those in the labourforce who are willing but not looking for work. 2) Those out of the labourforce who are not willing to work for reasons like carework, safety, restrictions etc.

Non-discouraged workers are those who are currently working, and those who are willing and have been looking for work in the past month.


## District of residence

```{r state}
tab_district <- df_disc %>% 
  group_by(area_actual, district_name) %>% 
  summarise(
    Total = n()
  )

tab_district_disc <- df_disc_only %>% 
  group_by(area_actual, district_name) %>% 
  summarise(
    `Number of discouraged` = n()
  ) %>% 
  left_join(tab_district) %>%
  mutate(
   Percentage = round(`Number of discouraged`/Total*100,2)
  )

write.csv(tab_district_disc, paste0(figures, "district"))
table_kable(tableframe = tab_district_disc ,caption = "Distribution of discouraged workers across districts")
```

The percentage of discouraged workers is lowest in the districts of Karnataka (where the LFP rates were highest).

## Age of the respondent

```{r age}

tab_age_disc <- tab_cross(df_disc_only, "area_actual","age_actual")
tab_age <- tab_cross(df_female_wob, "area_actual","age_actual") %>% 
  left_join(tab_age_disc, by = c("area_actual","age_actual"), suffix = c("", "_disc"))
tab_age_compare <- tab_age  %>% 
  mutate(share_dw = n_disc/n) %>% 
  select(-c(Percent, Percent_disc))

ggplot(data=tab_age, aes(x=age_actual, y=n, colour = area_actual)) +
  geom_smooth()+
  ggtitle("ALL")
ggplot(data=tab_age, aes(x=age_actual, y=n_disc, colour = area_actual)) +
  geom_smooth()+
  scale_y_continuous(limit = c(0,150))+
  ggtitle("Discouraged")
ggplot(data=tab_age_compare, aes(x=age_actual, y=share_dw, colour = area_actual)) +
  geom_smooth()+
  scale_y_continuous(limit = c(0,1))+
  ggtitle("Comparison")

tab_disc_age <- tab_crossXtreme(df_disc, "area_actual","disc_worker","age_actual") 
  
ggplot(data=tab_disc_age, aes(x=age_actual, y=Percent, colour = as.factor(disc_worker))) +
  geom_smooth()+
  scale_y_continuous(limit = c(0,4.5))+
  facet_grid("area_actual")+
  ggtitle("Discouraged workers vs the rest across sectors")
```


```{r education}
plot_list <- list("Social Category","Education", "Marital Status","religion", "Household Head", "Primary Income Earner", "Education of PIE","family_type", "children_household", "skill_training_recieved","drinking_water","house_type", "house_toilet", "electricity_connection", "jan_dhan_ac", "studying_household", "casual_daily_household", "permanent_work_household", "casual_piece_household", "knowledge_computer", "knowledge_smartphone", "knowledge_internet")
lapply(plot_list, plot_disc_area)
```


## Transport facility

```{r transport}
# tab_transport <- df_disc %>%
#  select(disc_worker, starts_with("transport")) %>%
#  select(-c(contains("specify"))) %>%
#  pivot_longer(
#    cols = starts_with("transport"),
#    names_to = "Mode",
#    values_to = "Number"
#  ) %>%
#  group_by(Mode, disc_worker) %>%
#  summarise(
#     preferred_transport = sum(Number),
#     Total = n(),
#     Percent = round(preferred_transport/Total*100, 1)
#  )
# 
# ggplot(tab_transport, aes(x=Mode, y=Percent, fill=disc_worker))+
#  geom_col(position = "dodge")+
#  scale_x_discrete(labels = str_wrap(tab_transport$Mode, width = 10), breaks = tab_transport$Mode)
# 
# tab_disc_transport <- df_disc %>%
#  select(disc_worker, area_actual, starts_with("transport")) %>%
#  select(-c(contains("specify"))) %>%
#  pivot_longer(
#    cols = starts_with("transport"),
#    names_to = "Mode",
#    values_to = "Number"
#  ) %>%
#  group_by(Mode, disc_worker, area_actual) %>%
#  summarise(
#     preferred_transport = sum(Number),
#     Total = n(),
#     Percent = round(preferred_transport/Total*100, 1)
#  )
# 
# ggplot(tab_disc_transport, aes(x=Mode, y=Percent, fill=disc_worker)) +
#  geom_col(position = "dodge")+
#  facet_grid(area_actual)

tab_transport <- df_disc %>% 
  select(starts_with("transport"), disc_worker, area_actual) %>% 
  select(-c(contains("specify"))) %>% 
  pivot_longer(
    cols = starts_with("transport"),
    names_to = "Modes",
    values_drop_na = T
  ) %>% 
  group_by(Modes,area_actual) %>%
  mutate(D = sum(value),
         Total_AT = n()) %>% 
  group_by(Modes,area_actual, disc_worker) %>% 
  summarise(
    D = first(D),
    Total_AT = first(Total_AT),
    C = sum(value),
    Percentage = round(C/D*100,1)) %>% 
  filter(disc_worker == 1)

ggplot(data = tab_transport %>% filter(area_actual != "Total"), mapping = aes(x = Modes, y = Percentage, fill = area_actual))+
  geom_col(position = "dodge")+
  geom_text(aes(label = Percentage),position=position_dodge(width=0.75), vjust=-0.25, size=2)+
  theme_bw() +
    scale_x_discrete(labels = wrap_format(12))+
    theme(axis.text = element_text(size = 7),
          axis.title = element_text(size = 7),
          plot.title = element_text(size = 9),
          legend.title = element_text(size = 7),
          legend.text = element_text(size = 6))+ 
    theme( legend.position = "bottom",
           strip.background = element_rect(colour="white"))

```

\newpage
## Forms of savings

```{r saving}
# tab_savings <- df_disc %>%
#   select(starts_with("savings"), disc_worker) %>%
#   select(-c(contains("specify"))) %>%
#   pivot_longer(
#     cols = starts_with("savings"),
#     names_to = "Form",
#     values_to = "Number",
#     values_drop_na = TRUE
#   ) %>%
#   group_by(Form, disc_worker) %>%
#   summarise(
#      Type = sum(Number),
#      Total = n(),
#      Percent = round(Type/Total*100, 1))
# 
# ggplot(tab_savings, aes(x=Form, y=Percent, fill=disc_worker))+
#  geom_bar(stat = "identity", position = "dodge")+
#  scale_x_discrete(labels = wrap_format(10))
# 
# tab_disc_savings <- df_disc %>%
#   select(starts_with("savings"), disc_worker, area_actual) %>%
#   select(-c(contains("specify"))) %>%
#   pivot_longer(
#     cols = starts_with("savings"),
#     names_to = "Form",
#     values_to = "Number",
#     values_drop_na = TRUE
#   ) %>%
#   group_by(Form, disc_worker, area_actual) %>%
#   summarise(
#      Type = sum(Number),
#      Total = n(),
#      Percent = round(Type/Total*100, 1))
# 
# ggplot(tab_savings, aes(x=Form, y=Percent, fill=disc_worker))+
#  geom_bar(stat = "identity", position = "dodge")+
#   facet_grid(area_actual)+
#  scale_x_discrete(labels = wrap_format(10))
# 
# table_kable(tableframe = tab_savings ,caption = "Different forms of savings by individuals")

tab_savings <- df_disc %>% 
  select(starts_with("savings"), disc_worker, area_actual) %>% 
  select(-c(contains("specify"))) %>% 
  pivot_longer(
    cols = starts_with("savings"),
    names_to = "Form",
    values_drop_na = T
  ) %>% 
  group_by(Form, area_actual) %>%
  mutate(D = sum(value),
         Total_AT = n()) %>% 
  group_by(Form, area_actual, disc_worker) %>% 
  summarise(
    D = first(D),
    Total_AT = first(Total_AT),
    C = sum(value),
    Percentage = round(C/D*100,1)) %>% 
  filter(disc_worker == 1)

ggplot(data = tab_savings %>% filter(area_actual != "Total"), mapping = aes(x = Form, y = Percentage, fill = area_actual))+
  geom_col(position = "dodge")+
  geom_text(aes(label = Percentage),position=position_dodge(width=0.75), vjust=-0.25, size=2)+
  theme_bw() +
    scale_x_discrete(labels = wrap_format(12))+
    theme(axis.text = element_text(size = 7),
          axis.title = element_text(size = 7),
          plot.title = element_text(size = 9),
          legend.title = element_text(size = 7),
          legend.text = element_text(size = 6))+ 
    theme( legend.position = "bottom",
           strip.background = element_rect(colour="white"))

```

\newpage
## Access to documents

```{r access}
# tab_documents <- df_disc %>%
#   select(starts_with("documents")) %>%
#   select(-c(contains("specify"))) %>%
#   pivot_longer(
#     cols = starts_with("documents"),
#     names_to = "Form",
#     values_to = "Number",
#     values_drop_na = TRUE
#   ) %>%
#   group_by(Form) %>%
#   summarise(
#      Type = sum(Number),
#      Total = n(),
#      Percent = round(Type/Total*100, 1))
# 
# table_kable(tableframe = tab_documents, caption = "")

tab_documents <- df_disc %>% 
  select(starts_with("documents"), disc_worker, area_actual) %>% 
  select(-c(contains("specify"))) %>% 
  pivot_longer(
    cols = starts_with("documents"),
    names_to = "Form",
    values_drop_na = T
  ) %>% 
  group_by(Form, area_actual) %>%
  mutate(D = sum(value),
         Total_AT = n()) %>% 
  group_by(Form, area_actual, disc_worker) %>% 
  summarise(
    D = first(D),
    Total_AT = first(Total_AT),
    C = sum(value),
    Percentage = round(C/D*100,1)) %>% 
  filter(disc_worker == 1)

ggplot(data = tab_documents %>% filter(area_actual != "Total"), mapping = aes(x = Form, y = Percentage, fill = area_actual))+
  geom_col(position = "dodge")+
  geom_text(aes(label = Percentage),position=position_dodge(width=0.75), vjust=-0.25, size=2)+
  theme_bw() +
    scale_x_discrete(labels = wrap_format(12))+
    theme(axis.text = element_text(size = 7),
          axis.title = element_text(size = 7),
          plot.title = element_text(size = 9),
          legend.title = element_text(size = 7),
          legend.text = element_text(size = 6))+ 
    theme( legend.position = "bottom",
           strip.background = element_rect(colour="white"))

```
## Cooking method
```{r food}
tab_cook <- df_disc %>% 
  select(starts_with("cooking"), disc_worker, area_actual) %>% 
  select(-c(contains("others"))) %>% 
  pivot_longer(
    cols = starts_with("cooking"),
    names_to = "Types",
    values_drop_na = T
  ) %>% 
  group_by(Types,area_actual) %>%
  mutate(D = sum(value),
         Total_AT = n()) %>% 
  group_by(Types,area_actual, disc_worker) %>% 
  summarise(
    D = first(D),
    Total_AT = first(Total_AT),
    C = sum(value),
    Percentage = round(C/D*100,1)) %>% 
  filter(disc_worker == 1)

ggplot(data = tab_cook %>% filter(area_actual != "Total"), mapping = aes(x = Types, y = Percentage, fill = area_actual))+
  geom_col(position = "dodge")+
  geom_text(aes(label = Percentage),position=position_dodge(width=0.75), vjust=-0.25, size=2)+
  theme_bw() +
    scale_x_discrete(labels = wrap_format(12))+
    theme(axis.text = element_text(size = 7),
          axis.title = element_text(size = 7),
          plot.title = element_text(size = 9),
          legend.title = element_text(size = 7),
          legend.text = element_text(size = 6))+ 
    theme( legend.position = "bottom",
           strip.background = element_rect(colour="white"))
  
```

## Types of assets owned
```{r assets}
tab_assets <- df_disc %>% 
  select(starts_with("personal_assets"), disc_worker, area_actual) %>% 
  select(-c(contains("others"))) %>% 
  pivot_longer(
    cols = starts_with("personal"),
    names_to = "Types",
    values_drop_na = T
  ) %>% 
  group_by(Types,area_actual) %>%
  mutate(D = sum(value),
         Total_AT = n()) %>% 
  group_by(Types,area_actual, disc_worker) %>% 
  summarise(
    D = first(D),
    Total_AT = first(Total_AT),
    C = sum(value),
    Percentage = round(C/D*100,1)) %>% 
  filter(disc_worker == 1)

ggplot(data = tab_assets %>% filter(area_actual != "Total"), mapping = aes(x = Types, y = Percentage, fill = area_actual))+
  geom_col(position = "dodge")+
  geom_text(aes(label = Percentage),position=position_dodge(width=0.75), vjust=-0.25, size=2)+
  theme_bw() +
    scale_x_discrete(labels = wrap_format(12))+
    theme(axis.text = element_text(size = 7),
          axis.title = element_text(size = 7),
          plot.title = element_text(size = 9),
          legend.title = element_text(size = 7),
          legend.text = element_text(size = 6))+ 
    theme( legend.position = "bottom",
           strip.background = element_rect(colour="white"))

```

<!-- ## Accessing bank account per month for withdrawals -->

<!-- ```{r withdraw-bank} -->
<!-- tab_withdrawal <- df_disc %>% mutate(access_bank_ac_withdrawal = as.factor(access_bank_ac_withdrawal)) %>% -->
<!--   tab_cross(.,"disc_worker", "access_bank_ac_withdrawal") -->
<!-- plotTwoVar(tab_withdrawal, "access_bank_ac_withdrawal","disc_worker") -->

<!-- ``` -->

<!-- ## Reasons of discouragement across Marital Status -->
<!-- ```{r marital-status} -->
<!-- tab22_married <- df_disc %>% -->
<!--   select(starts_with("wp22_work_not_willing"), Married) %>% -->
<!--   select(-c(contains("_rank_"), contains("others"))) %>% -->
<!--   pivot_longer(cols = starts_with("wp22"), -->
<!--                names_to = "Reasons", -->
<!--                values_drop_na = TRUE) %>% -->
<!--   group_by(Reasons) %>% -->
<!--   mutate( -->
<!--     Total = sum(value) -->
<!--   ) %>% -->
<!--   group_by(Married, Reasons) %>% -->
<!--   summarise( -->
<!--     Frequency = sum(value), -->
<!--     Percentage = round(Frequency/first(Total)*100,2) -->
<!--   ) %>% -->
<!--   pivot_wider(names_from = Married, -->
<!--               values_from =  c(Frequency, Percentage)) -->
<!-- table_kable(tableframe = tab22_married, caption = "Reasons for not willing to work") -->

<!-- tab23_married <- df_disc %>% -->
<!--   select(starts_with("wp23_quit"), Married) %>% -->
<!--   select(-c(contains("_rank_"), contains("_other"))) %>% -->
<!--   pivot_longer(cols = starts_with("wp23"), -->
<!--                names_to = "Reasons", -->
<!--                values_drop_na = T) %>% -->
<!--   group_by(Reasons) %>% -->
<!--   mutate( -->
<!--     Total = sum(value) -->
<!--   ) %>% -->
<!--   group_by(Married, Reasons) %>% -->
<!--   summarise( -->
<!--     Frequency = sum(value), -->
<!--     Percentage = round(Frequency/first(Total)*100,2) -->
<!--     ) %>% -->
<!--   pivot_wider(names_from = Married, -->
<!--               values_from =  c(Frequency, Percentage)) -->
<!-- table_kable(tableframe = tab23_married, caption = "Reasons for quitting work") -->
<!-- ``` -->

<!-- \newpage -->
<!-- ## Reasons for discouragement across social categories -->
<!-- ```{r social_category} -->
<!-- tab22_soc_cat <- tab22_factors(df_disc, "Social Category") -->
<!-- tab23_soc_cat <- tab23_factors(df_disc, "Social Category") -->
<!-- table_kable(tableframe = tab22_soc_cat, caption = "Reasons for not willing to work") -->
<!-- table_kable(tableframe = tab23_soc_cat, caption = "Reasons for quitting work") -->
<!-- ``` -->

<!-- \newpage -->
<!-- # Reasons for discouragement across Education levels -->
<!-- ```{r edu} -->
<!-- tab22_edu <- tab22_factors(df_disc, "Education") -->
<!-- tab23_edu <- tab23_factors(df_disc, "Education") -->
<!-- table_kable(tableframe = tab22_edu, caption = "Reasons for not willing to work") -->
<!-- table_kable(tableframe = tab23_edu, caption = "Reasons for quitting work") -->
<!-- ``` -->

<!-- \newpage -->
<!-- # Reasons for discouragement across family type -->
<!-- ```{r family} -->
<!-- table(df_disc$family_type) -->
<!-- tab22_fam_type <- tab22_factors(df_disc, "family_type") -->
<!-- tab23_fam_type <- tab23_factors(df_disc, "family_type") -->
<!-- table_kable(tableframe = tab22_fam_type, caption = "Reasons for not willing to work") -->
<!-- table_kable(tableframe = tab23_fam_type, caption = "Reasons for quitting work") -->
<!-- ``` -->



<!-- ```{r quitting} -->
<!-- tab23_reasons <- df_disc %>% -->
<!--   select(starts_with("wp23_quit"), disc_worker) %>% -->
<!--   select(-c(contains("_rank_"), contains("_other"))) %>% -->
<!--   pivot_longer(cols = starts_with("wp23"), -->
<!--                names_to = "Reasons", -->
<!--                values_drop_na = T) %>% -->
<!--   group_by(Reasons, disc_worker) %>% -->
<!--   mutate( -->
<!--     Total = sum(value) -->
<!--   ) %>% -->
<!--   group_by(Reasons, disc_worker) %>% -->
<!--   summarise( -->
<!--     Frequency = sum(value), -->
<!--     Percentage = round(Frequency/first(Total)*100,2)) -->

<!-- tab22_reasons <- df_disc %>% -->
<!--   select(starts_with("wp22_work_not_willing"), disc_worker) %>% -->
<!--   select(-c(contains("_rank_"), contains("_other"))) %>% -->
<!--   pivot_longer(cols = starts_with("wp2"), -->
<!--                names_to = "Reasons", -->
<!--                values_drop_na = T) %>% -->
<!--   group_by(Reasons, disc_worker) %>% -->
<!--   mutate( -->
<!--     Total = sum(value) -->
<!--   ) %>% -->
<!--   group_by(Reasons, disc_worker) %>% -->
<!--   summarise( -->
<!--     Frequency = sum(value), -->
<!--     Percentage = round(Frequency/first(Total)*100,2)) -->


<!-- ``` -->

